---
title: "RFOYTbp"
author: "Nicole Hack"
date: "August 1, 2017"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
  word_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup,include=F}
knitr::opts_chunk$set(echo = FALSE)

```

```{r, echo=F, include=F}
packages <- c('readxl','tidyverse','readr','data.table','dplyr','car','ggplot2','nortest','broom','ggsignif')
lapply(packages, require, character.only = T)
```

```{r, echo=FALSE, include=F, message=F}
#Load data sheets.
mrpl17<-read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-rpl17 -  Quantification Cq Results_0.csv")
mrpl17 <- mrpl17[mrpl17$Sample != 63,]#remove row 63 the only yellowtail 

mrb <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-rB -  Quantification Cq Results_0.csv")
mrb <- mrb[mrb$Sample != 63,]

mra <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-rA -  Quantification Cq Results_0.csv")
mra <- mra[mra$Sample != 63,]

migf2 <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-IGF2 -  Quantification Cq Results_0.csv")
migf2 <- migf2[migf2$Sample != 63,]

migf1 <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-IGF1 -  Quantification Cq Results_0.csv")
migf1 <- migf1[migf1$Sample != 63,]

mef1a <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-ef1a -  Quantification Cq Results_0.csv")
mef1a <- mef1a[mef1a$Sample != 63,]

mbp5b <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-BP5b -  Quantification Cq Results_0.csv")
mbp5b <- mbp5b[mbp5b$Sample != 63,]

mbp5a <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-BP5a -  Quantification Cq Results_0.csv")
mbp5a <- mbp5a[mbp5a$Sample != 63,]

mbp2b <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-BP2b -  Quantification Cq Results_0.csv")
mbp2b <- mbp2b[mbp2b$Sample != 63,]

mbp2a <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/RF muscle/RF muscle/YT-muscle-BP2a -  Quantification Cq Results_0.csv")
mbp2a <- mbp2a[mbp2a$Sample != 63,]

```

```{r, echo=F}
#Merge all data to get concentration by sample #
mbp2a$gene ='mbp2a'
mbp2b$gene = 'mbp2b'
mbp5a$gene = 'mbp5a'
mbp5b$gene = 'mbp5b'
mef1a$gene = 'mef1a'
migf1$gene = 'migf1'
migf2$gene = 'migf2'
mra$gene = 'mra'
mrb$gene = 'mrb'
mrpl17$gene = 'mrpl17'

dat_test = rbind(mbp2a, mbp2b,
                 mbp5a, mbp5b,
                 mef1a, 
                 migf1, migf2,
                 mra, mrb, mrpl17) %>%
  select(Sample, SQMean, gene) 

#Remove NAs
dat_test = filter(dat_test,!is.na(Sample) & SQMean != 0)


dat_test2 = dat_test %>%
  group_by(gene, Sample) %>%
  summarize(n = length(SQMean), Cq = mean(SQMean))

#output for Sean
mdata <- tidyr::spread(dat_test2,gene,Cq)
write.csv(mdata,'RFOLV-muscle.csv')
```

#Muscle data

```{r add treatment data, echo=F, warning=F}
RFOYTgrowth <- read.csv("~/RFOYT/RFOYT/RFOYTgrowth.csv")
#make new dataframe to play with
growth<-as.data.frame(RFOYTgrowth)

#reorganize data into long form
b = tidyr::gather(growth, 'data.type','value', 5:16) %>%
  select(PITtag, treatment)
colnames(b) = c('Sample', 'treatment')
b = unique(b)

dat_test3 = dplyr::left_join(dat_test2, b, by = 'Sample')
dat_test3 = filter(dat_test3, !is.na(Cq))

dat_test3$housekeeping = FALSE
dat_test3$housekeeping[dat_test3$gene == 'mef1a' | 
                         dat_test3$gene == 'mrpl17'] = TRUE

#find geometric mean of housekeepers and normalized Cq 
adj_Cq = plyr::ddply(dat_test3, 'Sample', function(x){
  target_genes = x[!x$housekeeping,]
  housekeeping_genes = x[x$housekeeping,]
  
  target_genes$mean_housekeeping = prod(housekeeping_genes$Cq)^(1/length(housekeeping_genes$Cq))#geometric mean
  
  target_genes$Cq_normalized = target_genes$Cq/target_genes$mean_housekeeping#normalize all genes to their geometric mean
  return(target_genes)
})

#Add new data of bp1
mbp1 <- read_excel("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/Lab results/RFOLVmuscleBP1aBP1b.xlsx")
mbp1.2 = tidyr::gather(mbp1,'gene','Cq_normalized',c(6,8))
mbp1.3 = mbp1.2[,c(2:3,7,8)] %>% dplyr::rename('Sample'='fish tag #')
adj_Cq = dplyr::union_all(adj_Cq,mbp1.3) 
adj_Cq = dplyr::filter(adj_Cq, !is.na(Cq_normalized))
```

```{r}

#Find mean for graphing
Cq = adj_Cq %>% group_by(gene, treatment) %>% summarize(mean_Cq = mean(Cq_normalized), sem_Cq =  sd(Cq_normalized)/sqrt(length(Cq_normalized)),n=length(Cq_normalized))

knitr::kable(Cq, caption = 'Summary table')

ggplot(adj_Cq, aes(y = Cq_normalized, x = gene, color = treatment))+
  geom_boxplot()
```


##Finding outliers

```{r Find outliers, echo=F}
#Look at housekeeper genes to make sure not too low or high
hk_Cq = dat_test3 %>% 
  filter(housekeeping == T) %>% 
  group_by(gene) %>% arrange(gene, Cq) 
refouts = rbind(top_n(hk_Cq,4,Cq), top_n(hk_Cq,-4,Cq)) %>% arrange(gene, Cq)
```

Top and bottom 4 values for both reference genes to determine accuracy.
```{r, echo= F, results='asis'}
knitr::kable(refouts, caption = "Reference genes")

```

Perhaps samples **113, 956, & 44** should be removed?

```{r, echo=F}
out = adj_Cq %>% group_by(gene,treatment) %>% summarize(max = max(Cq_normalized),min = min(Cq_normalized), max_sample = Sample[which(Cq_normalized == max)], min_sample = Sample[which(Cq_normalized == min)]) %>% arrange(min_sample)

knitr::kable(out,caption = 'Possible outliers of whole dataset')
```


**#972 & 103** for bp2b removed.

```{r}
adj_Cq <- adj_Cq %>% filter(!(gene == 'mbp2b' & (Sample == 103 | Sample == 972)))
#Find outliers
out_Cq = adj_Cq %>% group_by(gene) %>%
  filter(Cq_normalized < ((3*sd(Cq_normalized))+mean(Cq_normalized)) & Cq_normalized >( mean(Cq_normalized)-(3*sd(Cq_normalized))))

mremoved = adj_Cq %>% group_by(gene) %>%
  filter(Cq_normalized < (mean(Cq_normalized)-(3*sd(Cq_normalized))) |  Cq_normalized > ((3*sd(Cq_normalized))+mean(Cq_normalized)))
```

```{r, echo=F}

knitr::kable(mremoved, caption = 'Samples removed from statistics')
```

Removing **113 & 956**.

```{r}
out_Cq <- filter(out_Cq, Sample != 956 & Sample != 113) 

ggplot(out_Cq, aes(y = Cq_normalized, x = gene, color = treatment))+
  geom_boxplot()
```


---


```{r, echo=F}
#then run anova
myanova<-function(i){
  anova.genes<-lm(Cq_normalized~treatment,data=out_Cq,gene==i,na.action=na.omit)
}
anova.stats.m<- sapply(unique(out_Cq$gene), myanova, simplify=FALSE)
names(anova.stats.m)<-paste(unique(out_Cq$gene))#rename outputs to include days
capture.output(anova.stats.m, file = 'Muscle-gene-anova.txt')
```

##Statistics

```{r Manuscript graphs, echo=F}
knitr::kable(anova(anova.stats.m[[1]]), caption = 'BP2a')
knitr::kable(anova(anova.stats.m[[2]]), caption = 'BP2b')
knitr::kable(anova(anova.stats.m[[3]]), caption = 'BP5a')
knitr::kable(anova(anova.stats.m[[4]]), caption = 'BP5b')
knitr::kable(anova(anova.stats.m[[5]]), caption = 'IGF1')
knitr::kable(anova(anova.stats.m[[6]]), caption = 'IGF2')
knitr::kable(anova(anova.stats.m[[7]]), caption = 'Recepter A')
knitr::kable(anova(anova.stats.m[[8]]), caption = 'Recepter B')
knitr::kable(anova(anova.stats.m[[9]]), caption = 'BP1a')
knitr::kable(anova(anova.stats.m[[10]]), caption = 'BP1b')
```

bp5a, bp5b and igf1 are significant.

---


##Test for normality

Run Shapiro-Wilkes test for normality on residuals of linear model.
```{r Muscle graphs, echo=F}
#Check for normality

shapiro <- list()
for(n in 1:length(anova.stats.m)){
  test = shapiro.test(anova.stats.m[[n]]$residuals)
  test$data.name = names(anova.stats.m)[n]
  shapiro = cbind(shapiro, test)
}

knitr::kable(shapiro[c(1,2),], col.names = names(anova.stats.m))
```

bp1a, bp1b, bp2a, bp2b, igf1, and igf2 have non-normal residuals.

Looking at residuals for each gene.

```{r, echo=F, message=F}
ggplot(anova.stats.m[[1]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP2a')

ggplot(anova.stats.m[[2]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP2b')

ggplot(anova.stats.m[[5]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('IGF1')

ggplot(anova.stats.m[[6]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('IGF2')

ggplot(anova.stats.m[[9]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP1a')

ggplot(anova.stats.m[[10]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP1b')
```

bp2b, bp1a, & bp1b definitely have a positive skew. igf1 & 2 & bp2a have a slight positive skew but look normal overall.

---

###bp1a

Sqrt Cq and test for normality.

```{r, message=F}
bp1a = filter(out_Cq, gene == 'BP1a/ref') %>% mutate(new_Cq = sqrt(Cq_normalized))
test.log<- function(data){
   lmgene = lm(new_Cq~treatment, data = data)
   normality = shapiro.test(lmgene$residuals)
   hist = ggplot(lmgene, aes(x = .resid))+geom_histogram()
   return(list(normality, hist))
}
test.log(bp1a)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = bp1a))
```


---


###bp1b

Log Cq and test for normality.

```{r, message=F}
bp1b = filter(out_Cq, gene == 'BP1b/ref') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp1b)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = bp1b))
```


---

###bp2a

Sqrt Cq and test for normality.

```{r, message=F}
bp2a = filter(out_Cq, gene == 'mbp2a') %>% mutate(new_Cq = sqrt(Cq_normalized))
test.log(bp2a)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = bp2a))
```


---

###bp2b

Log Cq and test for normality.

```{r, message=F}
bp2b = filter(out_Cq, gene == 'mbp2b') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp2b)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = bp2b))
```


---

###igf1

Sqrt Cq.

```{r, message=F}
test.igf1 = filter(out_Cq, gene == 'migf1') %>% mutate(new_Cq = sqrt(Cq_normalized))
test.log(test.igf1)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = test.igf1))
```


---

###igf2

Log Cq.

```{r, message=F}
test.igf2 = filter(out_Cq, gene == 'migf2') %>% mutate(new_Cq = log(Cq_normalized))
test.log(test.igf2)
```


Retun stats on normalized migf2.

```{r}
anova(lm(Cq_normalized~treatment, data = test.igf2))
```


---

##Muscle Graphs

These graphs are *NOT* on normality corrected data. They do have all the recommended outliers removed.

```{r, echo=F}
#Convert mean to percent -> Set low mean per gene to 100%
#Find overall low mean and sem
low_mean = out_Cq %>% filter(treatment =='l')%>% group_by(gene)  %>% summarize(low_mean = mean(Cq_normalized))
cop = copy(low_mean)
low_mean = bind_rows(low_mean,cop) %>% arrange(gene) %>% as.list()
#Find mean for graphing
sum_Cq = out_Cq %>% group_by(gene, treatment) %>% summarize(mean_Cq = mean(Cq_normalized), sem_Cq =  sd(Cq_normalized)/sqrt(length(Cq_normalized)),n=length(Cq_normalized))
sum_Cq$low_mean = low_mean[[2]]#add to means table
sum_Cq = as.data.frame(sum_Cq) %>% mutate(new_mean = mean_Cq/low_mean)#Calculate percent by dividing by low mean
sum_Cq = as.data.frame(sum_Cq) %>% mutate(new_sem = sem_Cq/low_mean) %>% arrange(desc(treatment))#Calculate percent by dividing by  low sem

ggplot(sum_Cq, aes(x = gene, weight = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = treatment))+
  geom_bar(stat = 'identity', color = 'black', aes(y=new_mean),position=position_dodge())+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.9))+
  theme_classic(base_size = 18)
```

Separated graphs

```{r Separated muscle graphs, echo = F}
#separate for easier viewing
igfs = sum_Cq %>% filter(gene == 'migf1' | gene == 'migf2')
ggplot(igfs, aes(x = gene, weight = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = forcats::fct_rev(treatment)))+
  geom_bar(stat = 'identity', color = 'black',width = 0.6, aes(y=new_mean),position=position_dodge(width = 0.6))+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.6))+
  ylab('Relative mRNA level')+
  xlab('Gene')+
  coord_cartesian(ylim = c(0.5,2.6))+
  scale_x_discrete(labels = c("igf1","igf2"))+
  scale_fill_manual(values = c("#A9A9A9","#696969"), name = 'Treatment', labels = c('Low ration','High ration'))+
  geom_signif(aes(y = new_mean), y_position=2.5, xmin=0.8, xmax=1.2,annotation="***", tip_length=0, textsize = 8) +
  theme_classic(base_size = 20)+
  theme(axis.text.x = element_text(face = "italic", size = 22),axis.title.x = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"), axis.text.y = element_text(size = 22),legend.position = c(0.8,0.85))
ggsave(filename = 'Fig7a.tiff', width = 7, height = 5)

bps = sum_Cq %>% filter(gene != 'migf1' & gene != 'migf2' & gene != 'mra' & gene != 'mrb')
ggplot(bps, aes(x = gene, weight = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem,  fill = forcats::fct_rev(treatment)))+
  geom_bar(stat = 'identity', color = 'black',width = 0.6, aes(y=new_mean),position=position_dodge(width = 0.6))+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.6))+
  ylab('Relative mRNA level')+
  xlab('Gene')+
  scale_y_continuous(expand = c(0,0),limits = c(0,1.7))+
  scale_x_discrete(labels = c('igfbp1a','igfbp1b',"igfbp2a","igfbp2b",'igfbp5a','igfbp5b'))+
  scale_fill_manual(values = c("#A9A9A9","#696969"), name = 'Treatment', labels = c('High','Low'))+
  geom_signif(aes(y = new_mean), y_position=c(1.5,1.5), xmin=c(4.7, 5.7), xmax=c(5.2, 6.2),annotation=c("*", "**"), tip_length=0, textsize = 8) +
  theme_classic(base_size = 20)+
  theme(axis.text.x = element_text(face = "italic",size = 22, angle = 45, hjust=1), axis.text.y = element_text(size = 22),legend.position = 'none',axis.title.x = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"))
ggsave(filename = 'Fig7b.tiff', width = 7, height = 5)

receps = sum_Cq %>% filter(gene == 'mra' | gene == 'mrb')
ggplot(receps, aes(x = gene, y = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = forcats::fct_rev(treatment)))+
  geom_bar(stat = 'identity', color = 'black',width = 0.6, aes(y=new_mean),position=position_dodge(width = 0.6))+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.6))+
  ylab('Relative mRNA level')+
  xlab('Gene')+
  coord_cartesian(ylim = c(0.75,1.2))+
  scale_x_discrete(labels = c('igf1ra','igf1rb'))+
  scale_fill_manual(values = c("#A9A9A9","#696969"))+
  theme_classic(base_size = 20)+
  theme(axis.text.x = element_text(face = "italic", size = 22),axis.title.x = element_blank(),axis.text.y = element_text(size = 22),legend.position = 'none',plot.margin=unit(c(1,1,1.5,1.2),"cm"))
ggsave(filename = 'Fig7c.tiff', width = 7, height = 5)

```

Plasma and muscle mRNA igf1 correlation

```{r}
pigf <- read_csv("igf1.csv")[,2:3]#pulled plasma igf1 from growth data
migf <- filter(out_Cq, gene == 'migf1')#only want to look at correlation to igf1
cmigf1 <- inner_join(migf, pigf, by = c('Sample'='PITtag'))
cmigf1 <- filter(cmigf1, !is.na(IGF1))

cor.test(cmigf1$IGF1,cmigf1$Cq_normalized,method='pearson')

ggplot(cmigf1, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = c("#696969","#A9A9A9"), name = 'Treatment', labels = c('High ration', 'Low ration'))+
  geom_smooth(method = lm, color = 'black', se = F)+
  xlab('Plasma Igf1')+
  ylab(expression(paste('Relative muscle ',italic('igf1'), ' mRNA')))+
  theme_classic(base_size = 20)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'), legend.position = c(0.2,0.8),axis.text = element_text(size = 22))
ggsave(filename = 'Fig8.tiff', width = 7, height = 5)
```

High treatment

```{r}
cmigf1.h <- filter(cmigf1, treatment == 'h')

cor.test(cmigf1.h$IGF1, cmigf1.h$Cq_normalized, method = 'pearson')

ggplot(cmigf1.h, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = "#696969")+
  geom_smooth(method = lm, color = 'black', se = F)+
  xlab('')+
  ylab(expression(paste('Relative muscle ',italic('igf1'), ' mRNA')))+
  theme_classic(base_size = 20)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'), legend.position = 'none',axis.text = element_text(size = 22))
ggsave(filename = 'FigS2a.tiff', width = 7, height = 5)
```

Low treatment

```{r}
cmigf1.l <- filter(cmigf1, treatment == 'l')

cor.test(cmigf1.l$IGF1, cmigf1.l$Cq_normalized, method = 'pearson')

ggplot(cmigf1.l, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = "#A9A9A9")+
  xlab('Plasma Igf1')+
  ylab(expression(paste('Relative muscle ',italic('igf1'), ' mRNA')))+
  #xlim(10,30)+
  theme_classic(base_size = 20)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'), legend.position = 'none',axis.text = element_text(size = 22))
ggsave(filename = 'FigS2b.tiff', width = 7, height = 5)
```


---

#Liver data

```{r, include =F}
OLV_liver_mRNA <- read_csv("C:/Users/manic/Dropbox/Home computer/CalPoly/Rockfish/Lab results/OLV_liver_mRNA.csv")

liver <- OLV_liver_mRNA %>% select(PITtag,treatment,EF1a,rpl7,IGF1,IGF2,BP1a,BP1b,BP2a,BP2b,BP5a,BP5b)
liver<-liver %>% filter(PITtag != 63 & !is.na(EF1a))#remove #63 (yellowtail) and any with no geometric mean

#switch to long form
lrna=tidyr::gather(liver,'gene','Cq',3:12)

lrna['housekeeping'] = FALSE
lrna$housekeeping[lrna$gene == 'EF1a' | 
                         lrna$gene == 'rpl7'] = TRUE

lrna = filter(lrna, !is.na(Cq))

adj_livr = plyr::ddply(lrna, 'PITtag', function(x){
  target_genes = x[!x$housekeeping,]
  housekeeping_genes = x[x$housekeeping,]
  
  target_genes$mean_housekeeping = prod(housekeeping_genes$Cq)^(1/length(housekeeping_genes$Cq))
  
  target_genes$Cq_normalized = target_genes$Cq/target_genes$mean_housekeeping
  return(target_genes)
})

#Look at housekeeper genes to make sure not too low or high
hk_liv = lrna %>% 
  filter(housekeeping == T) %>% 
  group_by(gene) %>% arrange(gene, Cq) 
refouts.l = rbind(top_n(hk_liv,6,Cq), top_n(hk_liv,-6,Cq)) %>% arrange(gene, Cq)

```

All liver data

```{r, echo=F}
ggplot(adj_livr,aes(x = gene, y = Cq,color=treatment))+
  geom_boxplot()

knitr::kable(refouts.l, caption = 'Reference genes')
```

##Find outliers

```{r, echo=F}
#Find outliers
out_livr = adj_livr %>% group_by(gene) %>%
  filter((Cq_normalized < (3*sd(Cq_normalized)+mean(Cq_normalized))) & (Cq_normalized > (mean(Cq_normalized)-(3*sd(Cq_normalized)))))

removed = adj_livr %>% group_by(gene) %>%
  filter((Cq_normalized > (3*sd(Cq_normalized)+mean(Cq_normalized))) | (Cq_normalized <(mean(Cq_normalized)-(3*sd(Cq_normalized)))))

knitr::kable(removed, caption = 'Samples removed from std dev')

out = out_livr %>% group_by(gene,treatment) %>% summarize(max = max(Cq_normalized),min = min(Cq_normalized), max_sample = PITtag[which(Cq_normalized == max)], min_sample = PITtag[which(Cq_normalized == min)]) %>% arrange(max_sample)

knitr::kable(out, caption = 'Possible outliers')
```

Removing **#29, 50, 116, & 923** as discussed.

```{r}
ggplot(out_livr,aes(x = gene, y = Cq,color=treatment))+
  geom_boxplot()
```


##Statistics

```{r, echo=F}
out_livr = out_livr %>% filter(PITtag!=29 & PITtag!=50 & PITtag!=116 & PITtag != 923)

#Find mean for graphing
Cq_liv = out_livr %>% group_by(gene, treatment) %>% summarize(mean_Cq = mean(Cq_normalized), sem_Cq =  sd(Cq_normalized)/sqrt(length(Cq_normalized)),n=length(Cq_normalized))

#then run anova
myanova<-function(i){
  anova.genes<-lm(Cq_normalized~treatment,data=out_livr,gene==i,na.action=na.omit)
}
anova.stats.l <- sapply(unique(out_livr$gene), myanova, simplify=FALSE)
names(anova.stats.l)<-paste(unique(out_livr$gene))#rename outputs to include days

knitr::kable(anova(anova.stats.l[[1]]), caption = 'IGF1')
knitr::kable(anova(anova.stats.l[[2]]), caption = 'IGF2')
knitr::kable(anova(anova.stats.l[[3]]), caption = 'BP1a')
knitr::kable(anova(anova.stats.l[[4]]), caption = 'BP1b')
knitr::kable(anova(anova.stats.l[[5]]), caption = 'BP2a')
knitr::kable(anova(anova.stats.l[[6]]), caption = 'BP2b')
knitr::kable(anova(anova.stats.l[[7]]), caption = 'BP5a')
knitr::kable(anova(anova.stats.l[[8]]), caption = 'BP5b')
```

bp1a and bp1b are significant.

##Test for normality

Run Shapiro-Wilkes test for normality on residuals of linear model.
```{r Liver normality, echo=F}
#Check for normality

shapiro.l <- list()
for(n in 1:length(anova.stats.l)){
  test = shapiro.test(anova.stats.l[[n]]$residuals)
  test$data.name = names(anova.stats.l)[n]
  shapiro.l = cbind(shapiro.l, test)
}

knitr::kable(shapiro.l[c(1,2),], col.names = names(anova.stats.l))
```

Seems all are non-normal except igf1.

Looking at residuals for each gene.

```{r, echo=F, message=F}
ggplot(anova.stats.l[[2]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('IGF2')

ggplot(anova.stats.l[[3]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP1a')

ggplot(anova.stats.l[[4]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP1b')

ggplot(anova.stats.l[[5]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP2a')

ggplot(anova.stats.l[[6]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP2b')

ggplot(anova.stats.l[[7]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP5a')

ggplot(anova.stats.l[[8]], aes(x = .resid))+
  geom_histogram()+
  ggtitle('BP5b')
```

They seem to be all positive skewed with obvious outliers.

###igf2

Logging.

```{r, message=F}
logigf2 = filter(out_livr, gene == 'IGF2') %>% mutate(new_Cq = log(Cq_normalized))
test.log(logigf2)
```

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = logigf2))
```

Still not significant.

---

###bp1a

Logging.

```{r, message=F}
bp1al = filter(out_livr, gene == 'BP1a') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp1al)
```

Fixed!

Rerunning stats
```{r}
anova(lm(new_Cq~treatment, data = bp1al))
```

---

###bp1b

Logging.

```{r, message=F}
bp1bl = filter(out_livr, gene == 'BP1b') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp1bl)
```

Rerunning stats.
```{r}
anova(lm(new_Cq~treatment, data = bp1bl))
```

---

###bp2a

Logging.

```{r, message=F}
bp2al = filter(out_livr, gene == 'BP2a') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp2al)
```

Seems bimodal. I don't think excluding outliers will help.

---

###bp2b

Logging.

```{r, message=F}
bp2bl = filter(out_livr, gene == 'BP2b') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp2bl)
```

Rerunning stats.
```{r}
anova(lm(new_Cq~treatment, data = bp2bl))
```

---

###bp5a

Square rooting as the skew seems moderate.

```{r, message=F}
bp5al = filter(out_livr, gene == 'BP5a') %>% mutate(new_Cq = sqrt(Cq_normalized))
test.log(bp5al)
```

Rerunning stats.
```{r}
anova(lm(new_Cq~treatment, data = bp5al))
```

---

###bp5b

Logging.

```{r, message=F}
bp5bl = filter(out_livr, gene == 'BP5b') %>% mutate(new_Cq = log(Cq_normalized))
test.log(bp5bl)
```

Rerunning stats.
```{r}
anova(lm(new_Cq~treatment, data = bp5bl))
```

---

##Liver Graphs

```{r,echo=F}
#Convert mean to percent -> Set total low mean to 100%
#Find overall low mean and sem
low_mean = out_livr %>% filter(treatment =='l')  %>% group_by(gene)%>% summarize(low_mean = mean(Cq_normalized))
copliv = copy(low_mean) 
low_mean = bind_rows(low_mean,copliv) %>% arrange(gene) %>% as.list()
Cq_liv$low_mean = low_mean[[2]]#add to means table
Cq_liv = as.data.frame(Cq_liv) %>% mutate(new_mean = mean_Cq/low_mean)#Calculate percent by dividing by overall low mean
Cq_liv = as.data.frame(Cq_liv) %>% mutate(new_sem = sem_Cq/low_mean)#Calculate percent by dividing by overall low sem

ggplot(Cq_liv, aes(x = gene, y = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = treatment))+
  geom_bar(stat = 'identity', color = 'black', aes(y=new_mean),position=position_dodge())+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.9))+
  theme_classic(base_size = 18)
#separate for easier viewing
igfs.l = Cq_liv %>% filter(gene == 'IGF1' | gene == 'IGF2')
ggplot(igfs.l, aes(x = gene, weight = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = forcats::fct_rev(treatment)))+
  geom_bar(stat = 'identity', color = 'black',width = 0.6, aes(y=new_mean),position=position_dodge(width = 0.6))+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.6))+
  ylab('Relative mRNA level')+
  xlab('Gene')+
  coord_cartesian(ylim = c(0.75,1.2))+
  scale_x_discrete(labels = c("igf1","igf2"))+
  scale_fill_manual(values = c("#A9A9A9","#696969"), name = 'Treatment', labels = c('Low ration','High ration'))+
  theme_classic(base_size = 22)+
  theme(axis.text.x = element_text(face = "italic",size = 22),axis.title.x = element_blank(),plot.margin=unit(c(1,1,1.5,1.2),"cm"),axis.text.y = element_text(size = 22))
ggsave(filename = 'Fig5a.tiff', width = 7, height = 5)

bps.liv = Cq_liv %>% filter(gene != 'IGF1' & gene != 'IGF2')
ggplot(bps.liv, aes(x = gene, weight = new_mean, ymin=new_mean - new_sem, ymax=new_mean + new_sem, fill = forcats::fct_rev(treatment)))+
  geom_bar(stat = 'identity', color = 'black',width = 0.6, aes(y=new_mean),position=position_dodge(width = 0.6))+
  geom_errorbar(width = 0.25, position=position_dodge(width=0.6))+
  ylab('Relative mRNA level')+
  xlab('Gene')+
  scale_y_continuous(expand = c(0,0),limits = c(0,1.5))+
  scale_x_discrete(labels = c("igfbp1a","igfbp1b",'igfbp2a','igfbp2b','igfbp5a','igfbp5b'))+
  scale_fill_manual(values = c("#A9A9A9","#696969"), name = 'Treatment', labels = c('Low','High'))+
  geom_signif(aes(y = new_mean), y_position=c(1.4,1.3), xmin=c(0.7,1.7), xmax=c(1.3,2.3),annotation=c("**","***"),vjust = 0.2, tip_length=0, textsize = 6) +
  theme_classic(base_size = 20)+
  theme(axis.text.x = element_text(face = "italic", angle = 45, size = 22, hjust = 1),axis.text.y = element_text(size = 22),axis.title.x = element_blank(),legend.position = 'none',plot.margin=unit(c(1,1,1.5,1.2),"cm"))
ggsave(filename = 'Fig5b.tiff', width = 7, height = 5)
```

Plasma IGF1 and mRNA (#56 removed)

```{r}
pigf <- read_csv("igf1.csv")[,2:3]#pulled plasma igf1 from growth data
ligf <- filter(out_livr, gene == 'IGF1')#only want to look at correlation to liver igf1
cigf1 <- inner_join(ligf, pigf, by = 'PITtag')
cigf1 <- filter(cigf1, !is.na(IGF1) & PITtag != '56')

cor.test(cigf1$IGF1,cigf1$Cq_normalized,method='pearson')

ggplot(cigf1, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = c("#696969","#A9A9A9"), name = 'Treatment', labels = c('High ration', 'Low ration'))+
  geom_smooth(method = lm, color = 'black', se = F)+
  xlab('Plasma Igf1')+
  ylab(expression(paste('Relative liver ',italic('igf1'), ' mRNA')))+
  theme_classic(base_size = 22)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'), axis.text.y = element_text(size = 22),axis.text.x = element_text(size = 22),legend.position = c(0.85,0.15))
ggsave(filename = 'Fig6.tiff', width = 7, height = 5)
```

High treatment

```{r}
cigf1.h <- filter(cigf1, treatment == 'h')

cor.test(cigf1.h$IGF1, cigf1.h$Cq_normalized, method = 'pearson')

ggplot(cigf1.h, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = "#696969")+
  geom_smooth(method = lm, color = 'black', se = F)+
  xlab('')+
  ylab(expression(paste('Relative liver ',italic('igf1'), ' mRNA')))+
  theme_classic(base_size = 20)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'),axis.text.y = element_text(size = 22),axis.text.x = element_text(size = 22), legend.position = 'none')
ggsave(filename = 'FigS1a.tiff', width = 7, height = 5)
```

Low treatment

```{r}
cigf1.l <- filter(cigf1, treatment == 'l')

cor.test(cigf1.l$IGF1, cigf1.l$Cq_normalized, method = 'pearson')

ggplot(cigf1.l, aes(x = IGF1, y = Cq_normalized)) + 
  geom_point(aes(fill = treatment), shape = 21, size = 3) + 
  scale_fill_manual(values = "#A9A9A9")+
  geom_smooth(method = lm, color = 'black', se = F)+
  xlab('Plasma Igf1')+
  ylab(expression(paste('Relative liver ',italic('igf1'), ' mRNA')))+
  xlim(10,30)+
  theme_classic(base_size = 20)+
  theme(legend.background = element_rect(linetype = 'solid', size = 0.5, colour = 'black'),axis.text.x = element_text(size = 22), axis.text.y = element_text(size = 22), legend.position = 'none')
ggsave(filename = 'FigS1b.tiff', width = 7, height = 5)
```


